---
title: "HW6"
author: "Ruwen Zhou"
date: "11/30/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(patchwork)
library(modelr)
knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  echo = T,
  warning = F
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

Read in the data.
```{r}
homicide_df =
  read_csv("data/data-homicides-master/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    ),
    resolved = forcats::fct_relevel(resolved, "unsolved"),
    victim_age = as.numeric(victim_age),
    victim_sex = as.factor(victim_sex)
  ) %>%
  select(-city,-state,-victim_last,-victim_first,-lon,-lat) %>%
  filter(
    !str_detect(city_state, "Tulsa|Dallas|Phoenix|Kansas"),
    victim_race %in% c("White", "Black"),
    victim_sex %in% c("Male", "Female")
  ) %>%
  nest(c(-city_state))
```

Do linear regression
```{r}
homicide_df =
  homicide_df %>%
  mutate(log = map(
    .x = data,
    ~ glm(
      resolved ~ victim_age + victim_sex + victim_race,
      data = .x,
      family = binomial()
    )
  ),
  result  = map(log, broom::tidy)) %>%
  select(-data) %>%
  unnest(result) %>%
  mutate(ci = map2(.x = log,
                   .y = term,
                   ~ confint(.x, .y))) %>%
  select(city_state, term, estimate, ci) %>%
  filter(term == "victim_raceWhite")
homicide_df %>%
  head() %>%
  knitr::kable()
```

# Problem 2
Clean data
```{r}
weight_df =
  read_csv("data/birthweight.csv") %>%
  janitor::clean_names() %>%
  select(babysex, bhead, blength, bwt, gaweeks,malform) %>% 
  drop_na() %>% 
  relocate(bwt, everything()) %>% 
  mutate(
    babysex = case_when(babysex == 1 ~ "male",
                        babysex == 2 ~ "female") %>% 
      as.factor(),
    malform = as.factor(malform)
  )
weight_df
```
Regression Model
```{r}
model = lm(bwt ~ gaweeks, data = weight_df)
model
```
Show a plot of model residuals against fitted values 
```{r}
resid_plot =
weight_df %>% 
  add_residuals(model) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + 
  geom_violin()
pred_plot =
weight_df %>% 
  add_predictions(model) %>% 
  ggplot(aes(x = gaweeks, y = pred)) + 
  geom_point()
resid_plot
pred_plot
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
model_compare1 = lm(bwt ~ blength + gaweeks, data = weight_df)
model_compare2 = lm(bwt ~ bhead*blength*babysex, data = weight_df)
```

```{r}
compare_df =
  crossv_mc(weight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    model   = map(.x = train, ~lm(bwt ~ gaweeks, data = .x)),
    model_compare1  = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_compare2 = map(.x = train, ~lm(bwt ~ bhead*blength*babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_0 = map2_dbl(.x = model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_1    = map2_dbl(.x = model_compare1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = model_compare2, .y = test, ~rmse(model = .x, data = .y)))
compare_df %>% 
  select(.id,rmse_0,rmse_1,rmse_2)
```
```{r}
compare_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```



# Problem 3
data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```
```{r}
set.seed(1)
weather_bootstrap =
  bootstrap(weather_df, n = 5000, id = "strap_number") %>%
  mutate(strap = map(strap, as_tibble),
    md = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
    r_square = map2_dbl(.x = md, .y = strap, ~ modelr::rsquare(.x, .y)),
    md = map(md, broom::tidy)) %>%
  unnest(md) %>%
  select(strap_number, term, estimate, std_error = std.error, r_square)

weather_bootstrap %>% head() %>% knitr::kable()
```

Plot r square
```{r}
weather_bootstrap %>%
  distinct(strap_number, r_square) %>%
  ggplot(aes(x = r_square)) +
  geom_density()
```

Plot log(beta0 * beta1)
```{r}
weather_bootstrap %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  janitor::clean_names() %>%
  mutate(log_beta =
           log(tmin * intercept)) %>%
  ggplot(aes(x = log_beta)) +
  geom_density()
```










